INTELLIGENT SYSTEMS

### 2021-04-23 slides/slides_paper5.tex
some fixes

\begin{frame}{PROPOSED APPROACH - Identity Authentication}
    Unlike the recognition, the authentication problem aims to see if 
    two different inputs belong to the same subject. To do this, it is necessary 
    to calculate the Euclidean distances between the input data and the data 
    vectors present in the training set. Once this is done, the resulting vector 
    must be translated into probabilities that will be useful in order to 
    calculate two indices (Area Under Curve (AUC), Equal-Error-Rate 
    (EER)) that will be useful for evaluating the CNN network.
\end{frame}

@@

                \caption{Accuracy and F1-score (1 Task, 1 Sensor).}

@@

                \caption{Accuracy and F1-score (1 Task, + Sensor).}

@@

                    \caption{Accuracy and F1-score (+ Task, 1 Sensor).}

@@

                    \caption{Accuracy and F1-score (+ Task, + Sensor).}

>>>>

\begin{frame}{PROPOSED APPROACH - Identity Authentication}
    Unlike the recognition, the authentication problem aims to see if 
    two different inputs belong to the same subject. To do this, it is necessary 
    to calculate the Euclidean distances between the input data and the data 
    vectors present in the training set. Once this is done, the resulting vector 
    must be translated into probabilities that will be useful in order to 
    calculate two indexs (Area Under Curve (AUC), Equal-Error-Rate 
    (EER)) that will be useful for evaluating the CNN network.
\end{frame}

@@

                \caption{Accuracy and F1-score (1 Task, 1 Sensor). 3 Tasks - 2 Sensors - 6 CNNs.}

@@

                \caption{Accuracy and F1-score (1 Task, + Sensor). 1 CNN for each Task.}

@@

                    \caption{Accuracy and F1-score (+ Task, 1 Sensor). 2 CNNs, one for each 3 Tasks.}

@@

                    \caption{Accuracy and F1-score (+ Task, + Sensor). Only 1 CNN for all Tasks.}
